---
title: "WBE_nic_para_ace"
author: "Thanh Bui"
date: "2/22/2022"
output:
  word_document: default
  html_document: default
---
---
title: "Outlier_detection"
output:
  word_document: default
  html_document: default
---
#Loading package

```{r}
require(nortest)
require(tidyverse)
require(lubridate)
require(coin)
require(ggeasy)
require(table1)
library(car)
require(pgirmess)
require(patchwork)
library(mice); library(VIM)
library(compareGroups)
```
#Input data
```{r}
setwd("E:/WBE")
WBE = read.csv("Data_nicotine_ace_para.csv",header=T,na.strings = ".")
WBE= WBE%>%
  mutate(Date= mdy(Date),
         Period= as.factor(Period))
         
attach(WBE)
```
#Imputation
```{r}
aggr(WBE)
mWBE = mice(WBE, seed=123, printFlag=F)
WBE = complete(mWBE, action=1)
```

#Back-calculation of metabolites
```{r}
R15 =6029878/8053663 #Population aged 15+

WBE= WBE%>%
  mutate(Weekday= wday(Date,label=T,abbr = T),
         Weekday= factor(Weekday,levels=c("Mon","Tue","Wed","Thu","Fri","Sat","Sun")),
         NIC1load=NIC1*80000/400000,
         COT1load=COT1*80000/400000,
         HCOT1load=HCOT1*80000/400000,
         ACE1load=ACE1*80000/400000,
         PARA1load=PARA1*80000/400000,
         NIC2load=NIC2*85000/430000,
         COT2load=COT2*85000/430000,
         HCOT2load=HCOT2*85000/430000,
         ACE2load=ACE2*85000/430000,
         PARA2load=PARA2*85000/430000,
         COTmassavg= (COT1load+COT2load)/2,
         #COTmassavg15= (COT1load+COT2load)/(2*R15),
         ACEmassavg= (ACE1load+ACE2load)/2,
         PARAmassavg= (PARA1load+PARA2load)/2,
         NICabs_COT= COTmassavg*2.85,
         Tobacco_COT = NICabs_COT/(0.172*0.9*R15))
```
**Compare mass load in the 2 sites**
```{r}
WBEload= WBE%>%
  select(Period,NIC1load:PARA2load)
table1(~NIC1load+NIC2load+COT1load+COT2load+HCOT1load+HCOT2load+ACE1load+ACE2load+ PARA1load+PARA2load|Period, data= WBEload)
attach(WBEload)
wilcox.test(NIC1load, NIC2load)
wilcox.test(COT1load, COT2load)
wilcox.test(HCOT1load, HCOT2load)
wilcox.test(ACE1load, ACE2load)
wilcox.test(PARA1load, PARA2load)
```
**Compare average massload in 3 period and tobacco consumption**
```{r}
attach(WBE)
table1(~COTmassavg+ACEmassavg+PARAmassavg+ NICabs_COT+Tobacco_COT|Period, data= WBE)
#Nicotine
s= ggplot(WBE,aes(x= as.factor(Period),y=COTmassavg, fill=Period))+
  geom_boxplot()+ labs(y="Mass load of cotinine (mg/day/person)",x="Period")+
  theme_bw()+
  theme_classic()+
  geom_hline(aes(yintercept = mean(COTmassavg)), color="brown") +
  easy_remove_legend()+
  easy_remove_legend_title()
s
kruskal.test(COTmassavg~as.factor(Period),data=WBE)
kruskalmc(COTmassavg,as.factor(Period))


#Acesulfame

t= ggplot(WBE,aes(x= as.factor(Period),y=ACEmassavg, fill=Period))+
  geom_boxplot()+ labs(y="Mass load of acesulfame (mg/day/person)",x="Period")+ 
  theme_bw()+
  theme_classic()+
  geom_hline(aes(yintercept = mean(ACEmassavg)), color="brown") +
  easy_remove_legend()+
  easy_remove_legend_title()
t
kruskal.test(ACEmassavg~as.factor(Period),data=WBE)
kruskalmc(ACEmassavg,as.factor(Period))

#Paracetamol
u= ggplot(WBE,aes(x= as.factor(Period),y=PARAmassavg, fill=Period))+
  geom_boxplot()+ labs(y="Mass load of paracetamol (mg/day/person)",x= "Period")+ 
  theme_bw()+
  theme_classic()+
  geom_hline(aes(yintercept = mean(PARAmassavg)), color="brown") +
  easy_remove_legend()+
  easy_remove_legend_title()
u
kruskal.test(PARAmassavg~as.factor(Period),data=WBE)
kruskalmc(PARAmassavg,as.factor(Period))

s+t+u
ggsave("massload_in_3_periods.jpg", dpi=300)
```
*Compare mass load between two sites over 3 period*
```{r}
#Nicotine
NICmassload = WBEload%>%
  select(Period,COT1load,COT2load)%>%
  rename("Site 1"= COT1load, "Site 2"= COT2load)%>%
  gather(Location,Load,-Period)

a= ggplot(NICmassload,aes(x= Period,y= Load, fill= Location))+ geom_boxplot()+
  labs(y="Mass load of cotinine (mg/day/person)",x= "Period")+
  theme_bw()+
  theme_classic()+
  geom_hline(aes(yintercept = mean(Load)), color="brown")+
  easy_remove_legend()
##Period 1
NICcon1 = NICmassload %>%
  filter(Period == 1)
createTable(compareGroups(Location~Load, method= c(Load=2),data=NICcon1))
##Period 2
NICcon2 = NICmassload %>%
  filter(Period == 2)
createTable(compareGroups(Location~Load, method= c(Load=2),data=NICcon2))
##Period 3
NICcon3 = NICmassload %>%
  filter(Period == 3)
createTable(compareGroups(Location~Load, method= c(Load=2),data=NICcon3))


#Acesulfame
ACEmassload = WBEload%>%
  select(Period,ACE1load,ACE2load)%>%
  rename("Site 1"= ACE1load, "Site 2"= ACE2load)%>%
  gather(Location,Load,-Period)
b= ggplot(ACEmassload,aes(x= Period,y= Load, fill= Location))+ geom_boxplot()+
  labs(y="Mass load of acesulfame (mg/day/person)",x= "Period")+
  theme_bw()+
  theme_classic()+
  geom_hline(aes(yintercept = mean(Load)), color="brown")+
  easy_remove_legend()
##Period 1
ACEcon1 = ACEmassload %>%
  filter(Period == 1)
createTable(compareGroups(Location~Load, method= c(Load=2),data=ACEcon1))
##Period 2
ACEcon2 = ACEmassload %>%
  filter(Period == 2)
createTable(compareGroups(Location~Load, method= c(Load=2),data=ACEcon2))
##Period 3
ACEcon3 = ACEmassload %>%
  filter(Period == 3)
createTable(compareGroups(Location~Load, method= c(Load=2),data=ACEcon3))

#Paracetamol
PARAmassload = WBEload%>%
  select(Period,PARA1load,PARA2load)%>%
  rename("Site 1"= PARA1load, "Site 2"= PARA2load)%>%
  gather(Location,Load,-Period)
c= ggplot(PARAmassload,aes(x= Period,y= Load, fill= Location))+ geom_boxplot()+
  labs(y="Massload of paracetamol (mg/day/person)",x= "Period")+
  theme_bw()+
  theme_classic()+
  geom_hline(aes(yintercept = mean(Load)), color="brown")+
  easy_legend_at("right")+
  easy_remove_legend_title()
##Period 1
PARAcon1 = PARAmassload %>%
  filter(Period == 1)
createTable(compareGroups(Location~Load, method= c(Load=2),data=PARAcon1))
##Period 2
PARAcon2 = PARAmassload %>%
  filter(Period == 2)
createTable(compareGroups(Location~Load, method= c(Load=2),data=PARAcon2))
##Period 3
PARAcon3 = PARAmassload %>%
  filter(Period == 3)
createTable(compareGroups(Location~Load, method= c(Load=2),data=PARAcon3))


a+b+c
ggsave("massload_2sites_in_3_periods.jpg", dpi=300)
```



**Concentration and massloads of metabolites detected over 3 periods**
```{r}
metabolites=WBE%>%
  select(NIC1,NIC2,COT1,COT2,HCOT1,HCOT2,ACE1,ACE2,PARA1,PARA2)%>%
  gather("Biomarker", "Amount",c(NIC1,NIC2,COT1,COT2,HCOT1,HCOT2,ACE1,ACE2,PARA1,PARA2))
table1(~NIC1+NIC2+COT1+COT2+HCOT1+HCOT2+ACE1+ACE2+PARA1+PARA2|Period,data = metabolites)

ace = WBE%>%
  select(ACE1,ACE2, Period)%>%
  gather("Ace","Amount",-Period)
table1(~Amount|Period,data = ace)
```


**NIC/COT ratio and PARA/ACE ratio**
```{r}
NIC.COT12 = WBE %>%
  mutate(NIC1.COT1= NIC1/COT1,
         NIC2.COT2= NIC2/COT2)%>%
  select(Period, NIC1.COT1,NIC2.COT2)%>%
  gather(key = "Location", value ="NIC.COTs", c(NIC1.COT1,NIC2.COT2))
table1(~NIC.COTs|Period, data = NIC.COT12)

PARA.ACE = WBE%>%
  mutate(PARA.ACE1=PARA1/ACE1,
         PARA.ACE2=PARA2/ACE2)%>%
  select(Period,PARA.ACE1,PARA.ACE2)%>%
  gather(key = "Location", value ="PARA.ACEs", -Period)
table1(~PARA.ACEs|Period, data = PARA.ACE)
kruskal.test(PARA.ACEs~Period, data = PARA.ACE)
kruskalmc(PARA.ACE$PARA.ACEs,PARA.ACE$Period)
```



#Weekly variation
```{r}
#Nicotine
m=ggplot(WBE, aes(x=Weekday, y= NICabs_COT, fill= "pink"))+ geom_boxplot() + labs(y="Nicotine consumption (mg/day/person)",x=NULL)+
  geom_hline(aes(yintercept = mean(NICabs_COT)), color="blue") +
  theme_bw()+
  theme_classic()+
  easy_remove_legend()
  
m

kruskal.test(NICabs_COT~Weekday, data=WBE)
table1(~NICabs_COT+ Tobacco_COT|Weekday, data = WBE)
ggsave("Weekly_nicotine_use.jpg", dpi=300)
```

#Between periods
```{r}
#Nicotine
attach(WBE)
n= ggplot(WBE,aes(x= as.factor(Period),y=NICabs_COT, fill=Period))+
  geom_boxplot()+ labs(y="Nicotine consumption (mg/day/person)",x=NULL)+
  theme_bw()+
  theme_classic()+
  geom_hline(aes(yintercept = mean(NICabs_COT)), color="brown") +
  easy_remove_legend()+
  easy_remove_legend_title()
n
ggsave("Nicotine consumption.jpg",  dpi= 300)
kruskal.test(NICabs_COT~as.factor(Period),data=WBE)
kruskalmc(NICabs_COT,as.factor(Period))
table1(~NICabs_COT|Period, data= WBE)

```



